Geometrization of characters of smooth group schemes over finite fields with an application to types for supercuspidal representations

### 2016-03-02 followup.tex
Catching up

For use below, we recall some basic facts about the Heisenberg-Weil representation and make a conjecture about the geometrization of these representations.
We refer the reader to \cite{berndt-schmidt:98a} for more details.

Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to Z$, where $Z$ is a one-dimensional vector space over $\Fq$.
Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$.
Then $V^\sharp$ is a split extension of $V$ by $Z$.
Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$; this group acts on $V^\sharp$.
Then  is the Jacobi group. 
From the construction above, it is clear that $\Sp(V)\ltimes V^\sharp$ may be viewed as the $\Fq$-points of an algebraic group over $\Fq$; we will refer to that algebraic group as the Jacobi group.

Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to \EEx$. 
The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
% through the Egorov identity \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)}.\todo{Find better reference.}
Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$.

\begin{conjecture}\label{conj:Jacobi}
%Notation as above.
There is an equivariant Weil sheaf $\cs{W}_\psi$ on the Jacobi group such that 
\[
\trFrob{\cs{W}_\psi} = \trace(W_\psi).
\]
\end{conjecture}

@@

\begin{proposition}\label{prop:geotypes}
Let $(C,\rho)$ be a Yu type, constructed as in Section~\ref{ssec:review}.
Let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:models}.
Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Assume Conjecture~\ref{conj:Jacobi}.
Then there is a virtual Weil sheaf $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
\end{proposition}

@@

Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
Let $\cs{W}_{i+1}$ be the Weil sheaf promised by Conjecture~\ref{conj:Jacobi} on the Jacobi group such that
\[
\trFrob{\cs{W}_{i+1}} = \trace(W_{i+1}).
\]
Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
$\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.

>>>>

For use below, we recall some facts about the Heisenberg-Weil representation.

Let $V$ be a finite-dimensional vector space over a finite field $\Fq$ equipped with a symplectic paring $\langle\ ,\ \rangle : V\times V \to Z$, where $Z$ is a one-dimensional vector space over $\Fq$.
Let $V^\sharp$ be the Heisenberg group determined by $(Z, \langle\ ,\ \rangle)$.
Then $V^\sharp$ is a split extension of $V$ by $Z$.
Let $\Sp(V)$ be the symplectic group determined by the symplectic pairing $\langle\ ,\ \rangle$; this group acts on $V^\sharp$.
The group $\Sp(V)\ltimes V^\sharp$ is called the Jacobi group. 
From the construction above, it is clear that the Jacobi group may be viewed as the $\Fq$-points of an algebraic group over $\Fq$; we will refer to that algebraic group as the Jacobi group.

Let $\psi : Z \to \EEx$ be an additive character and let $\omega_\psi$ be the Heisenberg representation on $V^\sharp$ with central character $\psi : Z \to \EEx$. 
The Heisenberg representation determines a representation $\pi_{\psi}$ of $\Sp(V)$ with the same representation space as $\omega_\psi$ and with the defining property: for each $g\in \Sp(V)$, $\pi_\psi(g)$ determines an isomorphism of representations $\omega_\psi^g \to \omega_\psi$.
Let $W_\psi = \pi_\psi \ltimes \omega_\psi$ be the representation of the Jacobi group $\Sp(V)\ltimes V^\sharp$ given by $\omega_\psi$ and $\pi_\psi$.

It is one of the main results of \cite{Gurevich-Hadani:geometric_Weil}*{(1.3.1)} that there is a Weil sheaf $\cs{W}_\psi$ on the Jacobi group such that 
\[
\trFrob{\cs{W}_\psi} = \trace(W_\psi).
\]

@@

\begin{proposition}\label{prop:geotypes}
Let $(C,\rho)$ be a Yu type, constructed as in Section~\ref{ssec:review}.
Let $G^i = \Gr_{R}(\underline{G}^i)$ be the Greenberg transform of the smooth group scheme $\underline{G}^i$ appearing in Section~\ref{ssec:models}.
Assume $\pi_0(\underline{G}^0)_\Fq^\reductive)$ is cyclic.
Then there is a virtual Weil sheaf $\cs{A}$ on $G$ such that $\trFrob{\cs{A}} = \trace(\rho)$.
\end{proposition}

@@

Consider the Jacobi group $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ and the Heisenberg-Weil representation $W_{i+1}$ appearing in Section~\ref{ssec:models}.
Let $\cs{W}_{i+1}$ be the Weil sheaf on the Jacobi group, recalled in Section~\ref{ssec:Jacobi} such that
\[
\trFrob{\cs{W}_{i+1}} = \trace(W_{i+1}).
\]
Recall from Section~\ref{ssec:models} that $\Sp(V_{i+1})\ltimes V_{i+1}^\sharp$ is a quotient of the special fibre of the smooth group scheme $\underline{G}^{i} \ltimes \underline{J}^{i+1}$.
Let $\cs{W}_0^{i+1}$ be the Weil sheaf on the special fibre of $\underline{G}^{i} \ltimes \underline{J}^{i+1}$ obtained from $W_{i+1}$ by pullback. 
Let $\cs{W}_m^{i+1}$ be the Weil sheaf on $\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1})$ obtained from $\cs{W}_0^{i+1}$ by pullback along the affine morphism
$\Gr^{R}_m(\underline{G}^{i} \ltimes \underline{J}^{i+1}) \to \Gr^{R}_0(\underline{G}^{i} \ltimes \underline{J}^{i+1})$.
